# Intro to Data Science HW 8
##### Copyright Jeffrey Stanton, Jeffrey Saltz, and Jasmina Tacheva


```{r}
# Enter your name here: Yunhan Zhang
```

### Attribution statement: (choose only one and delete the rest)


```{r}
# 1. I did this homework by myself, with help from the book and the professor.
```

The chapter on **linear models** (“Lining Up Our Models”) introduces **linear predictive modeling** using the tool known as **multiple regression**. The term “multiple regression” has an odd history, dating back to an early scientific observation of a phenomenon called **“regression to the mean.”** These days, multiple regression is just an interesting name for using **linear modeling** to assess the **connection between one or more predictor variables and an outcome variable**. 


<br>In this exercise, you will **predict Ozone air levels from three predictors**.

A.	We will be using the **airquality** data set available in R. Copy it into a dataframe called **air** and use the appropriate functions to **summarize the data**. 


```{r}
air <- airquality
?airquality
summary(air)
```

B.	In the analysis that follows, **Ozone** will be considered as the **outcome variable**, and **Solar.R**, **Wind**, and **Temp** as the **predictors**. Add a comment to briefly explain the outcome and predictor variables in the dataframe using **?airquality**.


```{r}
# From May 1 1973 to September 30 1973, the average ozone is 42.13 ppb. Max is 168 ppb. Min is 1 ppb.
# The average solar.r is 185.9 lang. Max is 334 lang. Min is 7 lang.
# The average wind is 9.958 mph. Max is 20.7 mph. Min is 1.7 mph.
# The average temp is 77.88 F. Max is 97 F. Min is 56 F.
```

C.	Inspect the outcome and predictor variables – are there any missing values? Show the code you used to check for that.


```{r}
is.na(air)
# Yes, there are some missing values across four variables.
```

D.	Use the **na_interpolation()** function from the **imputeTS package** (remember this was used in a previous HW) to fill in the missing values in each of the 4 columns. Make sure there are no more missing values using the commands from Step C.


```{r}
library(imputeTS)
air$Ozone <- na_interpolation(air$Ozone)
air$Solar.R <- na_interpolation(air$Solar.R)
# I used this is.na(air) to exam all the missing values are disappeared.
```

E.	Create **3 bivariate scatterplots (X-Y) plots** (using ggplot), for each of the predictors with the outcome. **Hint:** In each case, put **Ozone on the Y-axis**, and a **predictor on the X-axis**. Add a comment to each, describing the plot and explaining whether there appears to be a **linear relationship** between the outcome variable and the respective predictor.


```{r}
library(ggplot2)
ggplot(data=air) +  aes(x=Solar.R, y=Ozone) + geom_point()
# Maybe? Not sure. But I assume it does not have linear relationship.
ggplot(data=air) +  aes(x=Wind, y=Ozone) + geom_point()
# Yes, it appears to be a negative linear relationship.
ggplot(data=air) +  aes(x=Temp, y=Ozone) + geom_point()
# Yes, it appears to be a positive linear relationship.
```
F.	Next, create a **simple regression model** predicting **Ozone based on Wind**, using the **lm( )** command. In a comment, report the **coefficient** (aka **slope** or **beta weight**) of **Wind** in the regression output and, **if it is statistically significant**, **interpret it** with respect to **Ozone**. Report the **adjusted R-squared** of the model and try to explain what it means. 


```{r}
questionf <- lm(Ozone ~ Wind, data = air)
summary(questionf)
# The slope is -4.5925 indicates that ozone is decreasing as wind is increasing.
# The R-squared is 0.2527 indicates that the wind factor account for 25.27% of Ozone.
```

G.	Create a **multiple regression model** predicting **Ozone** based on **Solar.R**, **Wind**, and **Temp**.<br> **Make sure to include all three predictors in one model – NOT three different models each with one predictor.**


```{r}
questiong <- lm(Ozone ~ Solar.R + Wind + Temp, data = air)
summary(questiong)
```

H.	Report the **adjusted R-Squared** in a comment – how does it compare to the adjusted R-squared from Step F? Is this better or worse? Which of the predictors are **statistically significant** in the model? In a comment, report the coefficient of each predictor that is statistically significant. Do not report the coefficients for predictors that are not significant.


```{r}
# The R-squared value increases tp 0.4207. This is better. Only the Wind and Temp are statistically significant in model. Wind's coefficient is -2.70. Temp's coefficient is 1.53.
```

I.	Create a one-row data frame like this: 


```{r}
predDF <- data.frame(Solar.R=290, Wind=13, Temp=61)
```

 and use it with the **predict( )** function to predict the **expected value of Ozone**:


```{r}
predict(questiong,predDF)
```

J.	Create an additional **multiple regression model**, with **Temp** as the **outcome variable**, and the other **3 variables** as the **predictors**. 

Review the quality of the model by commenting on its **adjusted R-Squared**.  


```{r}
questionj <- lm(Temp ~ Solar.R + Wind + Ozone, data = air)
summary(questionj)
# All three factors are statistically significant to the model; however, Ozone > Wind > Solar.R. The R-squared value of 0.403 indicates that the three factors account for 40.30% of Temp.
```